\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.tex
Intro paragraph for PBMC3k

In the field of single-cell studies, a common analytical task involves
clustering to identify groups of cells with similar expression profiles.
NLDR methods are commonly used to display clusters, and help to verify
the results. For example, \citet{chen2023} illustrates the use of UMAP
to identify clusters in Human Peripheral Blood Mononuclear Cells
(PBMC3k). There are \(2622\) single cells. First 9 principal components
are used to generate the UMAP. Figure~\ref{fig-NLDR-variety} (a) is the
reproduction of the published plot. The objective is to select a
reasonable UMAP layout, representing the non-linear structure of the
digit 1 dataset in \(10\text{-}D\).

>>>>

In the field of single-cell studies, a common analytical task involves
clustering to identify groups of cells with similar expression profiles.
NLDR methods are commonly used to display clusters, and help to verify
the results. For example, \citet{chen2023} illustrates the use of UMAP
to identify clusters in Human Peripheral Blood Mononuclear Cells
(PBMC3k). There are \(2622\) single cells. First 9 principal components
are used to generate the UMAP. Figure~\ref{fig-NLDR-variety} (a) is the
reproduction of the published plot. The objective is to select a
reasonable \gD{} layout, representing the three close clusters of the
PBMC3k dataset in \(9\text{-}D\)
(Figure~\ref{fig-model-pbmc-author-proj} (a2)).
